\textbf{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}

### 2023-05-03 manuscript/supp-mat.tex
Added artworks. Updated manuscript.

%TC:ignore
\documentclass{article}
\usepackage{caption}
\usepackage{xcolor, colortbl}
\definecolor{BLUELINK}{HTML}{0645AD}
\definecolor{DARKBLUELINK}{HTML}{0B0080}
\PassOptionsToPackage{hyphens}{url}
\usepackage[colorlinks=false]{hyperref}
% for linking between references, figures, TOC, etc in the pdf document
\hypersetup{colorlinks,
    linkcolor=DARKBLUELINK,
    anchorcolor=DARKBLUELINK,
    citecolor=DARKBLUELINK,
    filecolor=DARKBLUELINK,
    menucolor=DARKBLUELINK,
    urlcolor=BLUELINK
} % Color citation links in purple
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{naturalnames}{hyperref}

@@

\usepackage[margin=50pt]{geometry}
\usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
\usepackage{lmodern}
\usepackage{bm,bbold}
\usepackage{verbatim}
\usepackage{float}
\usepackage{listings, enumerate, enumitem}
\usepackage[export]{adjustbox}
\usepackage{tabu}
\usepackage{longtable}
\tabulinesep=0.6mm
\newcommand\cellwidth{\TX@col@width}
\usepackage{hhline}
\setlength{\arrayrulewidth}{1.2pt}
\usepackage{multicol,multirow,array}
\usepackage{etoolbox}
\AtBeginEnvironment{tabu}{\footnotesize}
\usepackage{booktabs}
\usepackage{graphicx}
\pdfinclusioncopyfonts=1

@@

\newcommand{\UniDimArray}[1]{\bm{#1}}
\newcommand{\BiDimArray}[1]{\bm{#1}}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Var}{\textrm{Var}}
\newcommand{\der}{\textrm{d}}
\newcommand{\e}{\textrm{e}}
\newcommand{\avg}[1]{\left< #1 \right>} % for average
\newcommand{\Ne}{N_{\textrm{e}}}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\textrm{fix}}}
\newcommand{\dn}{d_N}
\newcommand{\ds}{d_S}
\newcommand{\dnds}{\dn / \ds}
\newcommand{\Sphy}{S_{0}}
\newcommand{\Sphyclass}{\mathcal{C}}
\newcommand{\SphyMean}{\overline{\Sphy}}
\newcommand{\divDel}{\Sphy^{\text{d}}}
\newcommand{\divWeak}{\Sphy^{\text{n}}}
\newcommand{\divAdv}{\Sphy^{\text{b}}}
\newcommand{\PdivDel}{\proba \left[ \divDel \right]}
\newcommand{\PdivWeak}{\proba \left[ \divWeak \right]}
\newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}
\newcommand{\given}{\mid}
\newcommand{\Spop}{S}
\newcommand{\SpopMean}{\overline{\Spop}}
\newcommand{\polyDel}{\Spop^{\text{d}}}
\newcommand{\polyNeutral}{\Spop^{\text{n}}}
\newcommand{\polyAdv}{\Spop^{\text{b}}}
\newcommand{\PpolyDel}{\proba \left[ \polyDel \right]}
\newcommand{\PpolyNeutral}{\proba \left[ \polyNeutral \right]}
\newcommand{\PpolyAdv}{\proba \left[ \polyAdv \right]}

\title{\textbf{Empirical evidence for beneficial mutations that are not adaptive innovations in mammals}}

\author{
    \large
    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, D.~A. {Hartasánchez}$^{1}$, N. {Salamin}$^{1}$}\\
    \scriptsize $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
    \scriptsize $^{2}$Université de Lyon, Université Lyon 1, CNRS, VetAgro Sup, Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Villeurbanne, France \\
    \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
}

@@

    \section{Mutation-selection codon models}\label{sec:site-specific-mutation-selection-codon-models}
    In BayesCode (\url{https://github.com/ThibaultLatrille/bayescode}), mutation-selection codon models are obtained by running \textit{mutselomega} for 2000 points of MCMC with the options:
    \begin{scriptsize}
        \begin{verbatim}
 mutselomega ---omegashift 0.0 --ncat 30 -a my_alignment.phy -t my_tree.newick -u 2000 my_genename
        \end{verbatim}
    \end{scriptsize}
    The collection of site-specific fitness profiles ($\UniDimArray{F^{(i)}}, \forall i$) are then obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
    \begin{scriptsize}
        \begin{verbatim}
 readmutselomega --every 1 --until 2000 --burnin 1000 --ss my_genename
        \end{verbatim}
    \end{scriptsize}
    The gene-specific $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) is also obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
    \begin{scriptsize}
        \begin{verbatim}
 readmutselomega --every 1 --until 2000 --burnin 1000 --nuc my_genename
        \end{verbatim}
    \end{scriptsize}

@@

    \subsubsection{$\dnds$ and beneficial back-mutations}
    \begin{center}
        \captionof{table}{$\dnds$ of beneficial back-mutations.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population &             Species & Tajima $\theta_{\pi}$  & $\mathbb{P}_{div}[ S_0^{b} ]$ & $\omega $ & $\omega ( S_0^{d} )$ & $\omega ( S_0^{n} )$ & $\omega ( S_0^{b} )$ \\
            \midrule
            \endfirsthead

            \toprule
            Population &             Species & Tajima $\theta_{\pi}$  & $\mathbb{P}_{div}[ S_0^{b} ]$ & $\omega $ & $\omega ( S_0^{d} )$ & $\omega ( S_0^{n} )$ & $\omega ( S_0^{b} )$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            Equus c. &      Equus caballus &               $ 0.002$ &                      $ 0.118$ &  $ 0.147$ &             $ 0.075$ &             $ 0.823$ &             $ 1.203$ \\

@@

            Australia &        Capra hircus &               $ 0.003$ &                      $ 0.121$ &  $ 0.125$ &             $ 0.068$ &             $ 0.629$ &             $ 1.099$ \\
            France &        Capra hircus &               $ 0.004$ &                      $ 0.120$ &  $ 0.126$ &             $ 0.068$ &             $ 0.633$ &             $ 1.102$ \\
            Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                      $ 0.120$ &  $ 0.125$ &             $ 0.068$ &             $ 0.630$ &             $ 1.100$ \\
            Iran &        Capra hircus &               $ 0.004$ &                      $ 0.121$ &  $ 0.125$ &             $ 0.067$ &             $ 0.630$ &             $ 1.108$ \\
            Italy &        Capra hircus &               $ 0.004$ &                      $ 0.120$ &  $ 0.126$ &             $ 0.068$ &             $ 0.634$ &             $ 1.102$ \\
            Morocco &        Capra hircus &               $ 0.004$ &                      $ 0.122$ &  $ 0.125$ &             $ 0.067$ &             $ 0.631$ &             $ 1.112$ \\

@@

            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                      $ 0.122$ &  $ 0.133$ &             $ 0.071$ &             $ 0.696$ &             $ 1.397$ \\
            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                      $ 0.124$ &  $ 0.134$ &             $ 0.071$ &             $ 0.701$ &             $ 1.431$ \\
            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                      $ 0.124$ &  $ 0.134$ &             $ 0.071$ &             $ 0.699$ &             $ 1.422$ \\
            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                      $ 0.123$ &  $ 0.134$ &             $ 0.071$ &             $ 0.703$ &             $ 1.411$ \\
            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                      $ 0.123$ &  $ 0.134$ &             $ 0.071$ &             $ 0.699$ &             $ 1.419$ \\
            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                      $ 0.123$ &  $ 0.133$ &             $ 0.071$ &             $ 0.699$ &             $ 1.407$ \\
            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                      $ 0.125$ &  $ 0.134$ &             $ 0.070$ &             $ 0.704$ &             $ 1.447$ \\
            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                      $ 0.123$ &  $ 0.133$ &             $ 0.070$ &             $ 0.699$ &             $ 1.413$ \\
            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                      $ 0.123$ &  $ 0.134$ &             $ 0.071$ &             $ 0.699$ &             $ 1.410$ \\

@@

        \item Tajima $\theta$ is the synonymous diversity.
        \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).

@@

    \newpage
    \begin{center}
        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|}
            \toprule
            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) \\
            \midrule
            \endhead
            \midrule
            \multicolumn{7}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            Equus c. &      Equus caballus &               $ 0.002$ &                $ 0.307$ &        $ 0.182$ &              $ 0.133$ &           $  27.0$ \\
            Iran &          Bos taurus &               $ 0.005$ &                $ 0.298$ &        $ 0.164$ &              $ 0.122$ &           $  26.1$ \\
            Uganda &          Bos taurus &               $ 0.005$ &                $ 0.303$ &        $ 0.167$ &              $ 0.123$ &           $  26.6$ \\
            Australia &        Capra hircus &               $ 0.003$ &                $ 0.301$ &        $ 0.157$ &              $ 0.116$ &           $  26.4$ \\
            France &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
            Iran &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
            Italy &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
            Morocco &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
            Iran &          Ovis aries &               $ 0.007$ &                $ 0.266$ &        $ 0.179$ &              $ 0.138$ &           $  22.7$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                $ 0.268$ &        $ 0.178$ &              $ 0.137$ &           $  22.8$ \\
            Various &          Ovis aries &               $ 0.009$ &                $ 0.264$ &        $ 0.180$ &              $ 0.140$ &           $  22.5$ \\
            Morocco &          Ovis aries &               $ 0.007$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.303$ &        $ 0.172$ &              $ 0.126$ &           $  26.8$ \\
            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.305$ &        $ 0.172$ &              $ 0.126$ &           $  27.1$ \\
            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.172$ &              $ 0.125$ &           $  27.3$ \\
            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.306$ &        $ 0.172$ &              $ 0.125$ &           $  27.1$ \\
            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  27.0$ \\
            African &        Homo sapiens &               $ 0.003$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.9$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.238$ &              $ 0.185$ &           $  22.0$ \\
            European &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.8$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\

@@

        \item Tajima $\theta$ is the synonymous diversity.
        \item $\mathbb{P}_{div}[\Sphy > 0]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 0 ($\Sphy > 0$).
        \item $\dnds$ is the ratio of non-synonymous over synonymous divergence estimated for all the non-synonymous substitutions in the terminal branch.
        \item $\dn(\Sphy < 0) / \ds$ is the ratio of non-synonymous over synonymous divergence estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient lower than 0 ($\Sphy < 0$).

@@

        \item $R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 0) / \ds$.

@@

    We estimated that between 20 and 25\% of $\dnds$ is over-estimated ($R(\dnds)$), corresponding to beneficial back-mutation inflating the $\dnds$ statistic.

@@

            Equus c. &      Equus caballus &               $ 0.002$ &          $ 0.017$ &                   $ 0.046$ &                                          $ 0.378$ &                         $ 0.678$ &                      $ 0.256$ \\
            Iran &          Bos taurus &               $ 0.005$ &          $ 0.016$ &                   $ 0.040$ &                                          $ 0.402$ &                         $ 0.525$ &                      $ 0.211$ \\
            Uganda &          Bos taurus &               $ 0.005$ &          $ 0.016$ &                   $ 0.038$ &                                          $ 0.420$ &                         $ 0.610$ &                      $ 0.256$ \\

>>>>

%TC:ignore
\documentclass{article}
\usepackage{caption}
\usepackage{xcolor, colortbl}
\definecolor{LIGHTGREY}{gray}{0.9}
\definecolor{BLUELINK}{HTML}{0645AD}
\definecolor{DARKBLUELINK}{HTML}{0B0080}
\PassOptionsToPackage{hyphens}{url}
\usepackage[colorlinks=false]{hyperref}
% for linking between references, figures, TOC, etc in the pdf document
\hypersetup{colorlinks,
    linkcolor=DARKBLUELINK,
    anchorcolor=DARKBLUELINK,
    citecolor=DARKBLUELINK,
    filecolor=DARKBLUELINK,
    menucolor=DARKBLUELINK,
    urlcolor=BLUELINK
} % Color citation links in purple
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{naturalnames}{hyperref}

@@

\usepackage[margin=50pt]{geometry}
\usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
\usepackage{lmodern}
\usepackage{bm,bbold}
\usepackage{verbatim}
\usepackage{float}
\usepackage{listings, enumerate, enumitem}
\usepackage[export]{adjustbox}
\usepackage{tabu}
\usepackage{longtable}
\tabulinesep=0.6mm
\newcommand\cellwidth{\TX@col@width}
\usepackage{hhline}
\setlength{\arrayrulewidth}{1.2pt}
\usepackage{multicol,multirow,array}
\usepackage{etoolbox}
\AtBeginEnvironment{tabu}{\footnotesize}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{orcidlink}
\usepackage{graphicx}
\pdfinclusioncopyfonts=1

@@

\newcommand{\UniDimArray}[1]{\bm{#1}}
\newcommand{\der}{\text{d}}
\newcommand{\e}{\text{e}}
\newcommand{\Ne}{N_{\text{e}}}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\text{fix}}}
\newcommand{\dn}{d_N}
\newcommand{\ds}{d_S}
\newcommand{\dnds}{\dn / \ds}
\newcommand{\Sphy}{S_{0}}
\newcommand{\SphyMean}{\overline{\Sphy}}
\newcommand{\SphyDel}{\mathcal{D}_0}
\newcommand{\SphyNeu}{\mathcal{N}_0}
\newcommand{\SphyBen}{\mathcal{B}_0}
\newcommand{\Sphyclass}{x}
\newcommand{\SphyclassAlt}{y}
\newcommand{\given}{\mid}
\newcommand{\Spop}{S}
\newcommand{\SpopDel}{\mathcal{D}}
\newcommand{\SpopNeu}{\mathcal{N}}
\newcommand{\SpopBen}{\mathcal{B}}
\newcommand{\ProbaPopDel}{\proba [ \SpopDel]}
\newcommand{\ProbaPopNeu}{\proba [ \SpopNeu ]}
\newcommand{\ProbaPopBen}{\proba [ \SpopBen ]}
\newcommand{\AdvMean}{\beta_b}
\newcommand{\DelMean}{\beta_d}
\newcommand{\thetaSyn}{\theta_{\text{S}}}

\title{\textbf{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}}

\author{
    \large
    \textbf{T. {Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J. {Joseph}$^{2\dag}$\orcidlink{0009-0002-1312-9930}, D.~A. {Hartasánchez}$^{1}$\orcidlink{0000-0003-2596-6883}, N. {Salamin}$^{1}$\orcidlink{0000-0002-3963-4954}}\\
    \scriptsize $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
    \scriptsize $^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France \\
    \scriptsize $^{\dag}$These authors contributed equally to this work\\
    \normalsize \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
}

@@

    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}

    \subsection{Mutation-selection codon models}
    \label{sec:site-specific-mutation-selection-codon-models}
    In \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
    \begin{scriptsize}
        \begin{verbatim}
 mutselomega ---omegashift 0.0 --ncat 30 -a my_alignment.phy -t my_tree.newick -u 2000 my_genename
        \end{verbatim}
    \end{scriptsize}
    The collection of site-specific fitness profiles ($\UniDimArray{F^{(i)}}, \forall i$) are then obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
    \begin{scriptsize}
        \begin{verbatim}
 readmutselomega --every 1 --until 2000 --burnin 1000 --ss my_genename
        \end{verbatim}
    \end{scriptsize}
    The gene-specific $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) is also obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
    \begin{scriptsize}
        \begin{verbatim}
 readmutselomega --every 1 --until 2000 --burnin 1000 --nuc my_genename
        \end{verbatim}
    \end{scriptsize}

@@

    \subsubsection{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$)}
    \begin{center}
        \captionof{table}{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$).}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population &             Species & Watterson's $\thetaSyn$  & $\proba_{div}[ \SphyBen ]$ & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &            $ 0.075$ &                $ 0.823$ &           $ 1.203$ \\

@@

            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.068$ &                $ 0.629$ &           $ 1.099$ \\
            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.633$ &           $ 1.102$ \\
            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &            $ 0.068$ &                $ 0.630$ &           $ 1.100$ \\
            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.067$ &                $ 0.630$ &           $ 1.108$ \\
            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.634$ &           $ 1.102$ \\
            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &            $ 0.067$ &                $ 0.631$ &           $ 1.112$ \\

@@

            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &            $ 0.071$ &                $ 0.696$ &           $ 1.397$ \\
            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.701$ &           $ 1.431$ \\
            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.422$ \\
            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.703$ &           $ 1.411$ \\
            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.419$ \\
            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.071$ &                $ 0.699$ &           $ 1.407$ \\
            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.070$ &                $ 0.704$ &           $ 1.447$ \\
            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.070$ &                $ 0.699$ &           $ 1.413$ \\
            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.410$ \\

@@

        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
        \item $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
        \item $\dn(\SphyNeu) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
        \item $\dn(\SphyBen) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.

@@

    \subsubsection{$\dnds$ over-estimation due to beneficial back-mutations}
    \begin{center}
        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|}
            \toprule
            Population & Species & Watterson's $\thetaSyn$ & $\proba_{div}[\Sphy > 1]$ & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{7}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &           $ 0.131$ &     $  10.5$ \\
            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &           $ 0.117$ &     $  11.1$ \\
            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.9$ \\
            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &           $ 0.111$ &     $  11.0$ \\
            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.671$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.516$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.598$ \\
            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &           $ 0.134$ &     $ 9.439$ \\
            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.582$ \\
            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &           $ 0.118$ &     $  11.2$ \\
            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.5$ \\
            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.799$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.780$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.768$ \\
            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.728$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.788$ \\

@@

        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
        \item $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.

@@

        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.

@@

    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to beneficial back-mutation inflating the $\dnds$ statistic.

@@

            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.010$ &                                          $ 1.395$ &                         $ 0.580$ &                      $ 0.809$ \\
            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.041$ &                                          $ 0.323$ &                         $ 0.857$ &                      $ 0.277$ \\
            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.013$ &                                          $ 0.991$ &                         $ 0.488$ &                      $ 0.483$ \\
